Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-07 opex2013_reply.tex
Last fixes by Yoav and proof reading of the new sections by me.
updated the reply to reviewers

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{datetime}
\usepackage{nicefrac}

@@

\vspace{0.5cm}
\noindent
To:\\
Dr. James Churnside,\\
Editor,\\
Associate Editor, Optics Express\\[0.6cm]

@@

\vspace{0.6cm}
Amit Aides and Yoav Schechner\\

@@

We would like to thank the reviewers for their general approval. In
the following we describe the changes made to the manuscript following
their remarks. Each reviewer's comment is summarized (colored in
blue), followed by our reply.

@@

\item \textcolor{blue}{ ``The paper can be devided in two parts, one
    for computing single scattering, the other for multiple
    scattering. While the first part can be treated by a simple
    inverse transformation sampling as presented by the authors, the
    second part should have a different more complex inversion. For
    this reason I think that larger errors arise in multiple
    scattering. I feel the authors should dedicate some time to review
    this second part, that is more realistic."}

  {}

@@

@@

  {There is no contradiction. The notation $F^{-1}$ refers to the
    inverse function of function $F$ and not to $\nicefrac{1}{F}$}

@@

  {Following the reviewer's comment, we have defined $\mu$ after
    Eq.~5, and revised the definition of the term ``voxel''. }

@@

  {}

@@

  {}

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{datetime}
\usdate
\usepackage{nicefrac}

%% fonts
\usepackage{mathptmx,courier,textcomp}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xfrac}

\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}

%
% Some new commands I use in this text
%
% Note:
% Nice curly font is {\bm{\mathcal{D}}}
%
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\abbrev}[1]{\rm{#1}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
\newcommand{\fix}[2]{\st{#1}\hl{#2}}

%
% Used symbols (only partial for now...)
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
\newcommand{\OpDistance}{\bm{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\MaskSun}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
\newcommand{\OpDiag}[1]{\mathbb{D}\left\{#1\right\}}
\newcommand{\DistSet}{\mathcal{C}}
\newcommand{\DistUnknown}{\vect{n}}
\newcommand{\DistEstimated}{\hat{\vect{n}}}
\newcommand{\CostFunc}[1]{E(#1)}

@@

\vspace{0.5cm}
\noindent
To:\\
Dr. James Churnside,\\
Associate Editor, Optics Express\\[0.6cm]

@@

\vspace{0.6cm}
Amit Aides, corresponding author.\\

@@

We would like to thank the reviewers for their general approval and useful
suggestions. In the following we describe the changes made to the manuscript
following their remarks. Each comment is summarized (colored in
blue), followed by our reply.

@@

\item \textcolor{blue}{ ``The paper can be divided in two parts, one
    for computing single scattering, the other for multiple
    scattering. While the first part can be treated by a simple
    inverse transformation sampling as presented by the authors, the
    second part should have a different more complex inversion. For
    this reason I think that larger errors arise in multiple
    scattering. I feel the authors should dedicate some time to review
    this second part, that is more realistic."}

  {
    In this article we describe a novel data acquisition system
    and suggest a method to recover the 3D atmosphere based on
    the single-scattering approximation. Following the reviewer's
    suggestion we expanded our reference to the implications
    of high order scattering on our method.

    We added the new Fig.~5. In this figure we visually demonstrate
    the extents to which the single-scattering approximation is valid
    and to which it is not.

    The newly added Fig.~6 shows the contribution of each scattering order to
    the final MC image. Figure~6 makes clear that there are regions in
    the image that are affected by multiple scattering more than others.
    The two new paragraphs at the end of Sec.~6 reference the issues
    raised by Fig.~5 and Fig.~6.

    In the top of p.~10 we added a new description of $MaskSun$. We use
    $MaskSun$ to mask the regions in the image which are dominated 
    by multi-scattering as shown by Fig.~6. This method improves the
    results of the reconstruction algorithm.

    We test our reconstruction algorithm on a new scene where we
    increase the aerosol density tenfold. This significantly increases the
    effects of high order scattering. The results are shown in 
    Figs.~9(d) and 10(c), and reported in Table~1.
    Paragraph ``Density scale'' in Sec.~8 summarizes this experiment.
    Further discussion is given in Sec.~9.
  }

@@

\newpage

@@

  {The notation $F^{-1}$ refers to the inverse function
   of function $F$ and not to $\nicefrac{1}{F}$. Following the
   reviewer's comment we added a clarification in the ``Inverse
   transform sampling'' paragraph on p.~4. }

@@

  {We thank the reviewer for turning our attention to this.
   We replaced $\mu$ in Eq.~5 with its definition,
   $\cos \Phi^{\rm scatter}$. We revised the definition
   of the term ``voxel'', at the beginning of Sec.~4 of the
   article.}

@@

  {
    We appreciate the reviewer's comment. We added new simulations to
    test the effect of varying different properties of the aerosols.
    These experiments are detailed in Sec.~8. The results are shown
    in Figs.~9 and 10 and reported in Table.~1.
  }

@@

  {Following this comment, we repeated the reconstruction
   simulations many times, each time varying the distance between
   cameras. These tests are described in the paragraph ``Density of viewpoints''
   in Sec.~8. The results are shown in Fig.~8.}
